---
title: "Musk"
author: "Àlex Batlle, Luis Sierra, Aleix Torres"
date: "4/10/2020"
output: html_document
---

```{r}
data <- read.table("clean2.data", sep=',')
head(data)
```

Do not run this chunk, it takes too long simce the model has too many variables.

```{r}
giant_model <- glm(V169 ~ ., family = binomial, data = data)
summary(giant_model)
```

This what a couple of molecules look like, since there are many configurations for the same molecule.

```{r}
Musk.211 <- data[data$V1 == "MUSK-211",]
Musk.212 <- data[data$V1 == "MUSK-212",]
Musk.213 <- data[data$V1 == "MUSK-213",]
```

GLM using a small number of the variables.

```{r}
mod.simple <- glm(V169 ~ V3 + V4 + V5 + V6 + V7 + V8 + V9 + V10 + V11 + V12 + V13 + V14 + V15 + V16 + V17 + V18 + V19 + V20, family = binomial, data = data)
summary(mod.simple)
step(mod.simple)
```

Dimensionality reduction using PCA.

```{r}
out.PCA <- princomp(data[3:169])
summary(out.PCA)
```

GLM from results of PCA

```{r}
library(tidyverse)
set.seed(1234) #repro

data_ <- as_tibble(data)

pca <- FactoMineR::PCA(data_[-1:-2], graph = FALSE)

score <- as_tibble(factoextra::get_pca_ind(pca)$coord) #extract individual scores

model <- cbind(data_[169], score[1:5]) #use V1 as DV, use Dim.1:Dim.2 as IV

glm <- glm(V169 ~ Dim.1 + Dim.2+ Dim.3 + Dim.4 + Dim.5, family = binomial, data = model)
summary(glm)
step(glm)
```

LDA

```{r}
library(MASS)
#plot(data[, c(4, 7)], col = data[,169] + 2) #Ridiculous
data.lda <- lda(V167 ~ V1 + V2 + V3 + V4 + V5, data = data)
plot(data.lda)
```

#### Model Evaluation:

We could implement LOOCV. Below we separate the data into training and testing to evaluate the performance of the models, in an 8:2 training/testing ratio.

```{r}
library(magrittr)
library(caret)
set.seed(123)

# Function to separate into training data and test data
sample_size <- floor(0.80 * nrow(data))
train_indices <- sample(seq_len(nrow(data)), size = sample_size)
train.data  <- data[train_indices, ]
test.data <- data[-train_indices, ]
# Now define the models using only the training data and evaluate performance through testing

# GLM model consisting of logistic regression from the first 10 variables
simple10_glm_model <- glm(V169 ~ V3 + V4 + V5 + V6 + V7 + V8 + V9 + V10 + V11 + V12, family = binomial, data = train.data)
prob_predictions <- simple10_glm_model %>% predict(test.data, type = "response")
predicted.classes <- ifelse(prob_predictions > 0.5, 1, 0)
mean(predicted.classes == test.data$V169) # Accuracy of prediction

# GLM model consisting of a logistic regression from the first 20 variables
simple20_glm_model <- glm(V169 ~ V3 + V4 + V5 + V6 + V7 + V8 + V9 + V10 + V11 + V12 + V13 + V14 + V15 + V16 + V17 + V18 + V19 + V20 + V21 + V22, family = binomial, data = train.data)
prob_predictions <- simple20_glm_model %>% predict(test.data, type = "response")
predicted.classes <- ifelse(prob_predictions > 0.5, 1, 0)
mean(predicted.classes == test.data$V169) # Accuracy of prediction
```




